### 2021-04-28 evaluation.tex
Add a todo comment
consistent cref
trochu lepsi popis strategies

We run \Vampire{} with a fixed strategy\footnote{
Saturation algorithm: discount,
age-weight ratio: 1:10,
AVATAR \cite{Voronkov2014}: disabled,
literal comparison mode: predicate
}
and a time limit of 10 seconds.
To increase the potential impact of predicate precedences,
we used a simple \gls{tkbo} \cite{Ludwig2007,Kovacs2011}
that compares atoms according to the predicate precedence first,
using the regular \gls{kbo} to break ties between atoms
and to compare terms (using the \Vampire{} option \texttt{-{}-literal\_comparison\_mode predicate}).\todo{MS: ted s vysvetlenim neni naskodu zminit i option name 
``Vampire'' se tim chlubi, ze to ma naimplementovane a my tim rikame, ze jsme si to neprogramovali sami.}

@@

We employed adaptive sampling to balance
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator kept track of the number of times the problem has been tried $n_P$,
and the number of examples generated from that problem $s_P$.
The ratio $\frac{s_P}{n_P}$ corresponded to the average reward of problem $P$ observed so far.
The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
% FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.

@@

To generate a precedence for a problem,
\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit of 10 seconds was only imposed on the \Vampire{} run,
excluding the time taken by the recommender to generate the precedence.
When run with 2 threads,
the preprocessing of a single problem
took at most \num[round-mode=places,round-precision=2]{1.263048204} seconds
for \SI{80}{\percent} of the problems
by extrapolation from a sample of \num{1000} problems.\footnote{The remaining \SI{20}{\percent} of the problems either finished preprocessing within 5 seconds, or were omitted from preprocessing due to exceeding the node count limit.}
% \num[round-mode=places,round-precision=2]{4.745481158}
\todo[author=FB]{Is the footnote with maximum observed time worth the space?}
% Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
% VML-715
\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
\Cref{tab:results} shows the results of the final evaluation.

>>>>

We run \Vampire{} with a fixed strategy\footnote{
Saturation algorithm: DISCOUNT,
age to weight ratio: 1:10,
AVATAR \cite{Voronkov2014}: disabled,
literal comparison mode: predicate; all other options left at their default values.
}
and a time limit of 10 seconds.
To increase the potential impact of predicate precedences,
we used a simple \gls{tkbo} \cite{Ludwig2007,Kovacs2011}
that compares atoms according to the predicate precedence first,
using the regular \gls{kbo} to break ties between atoms
and to compare terms (using the \Vampire{} option \texttt{-{}-literal\_comparison\_mode predicate}).\todo{MS: ted s vysvetlenim neni naskodu zminit i option name 
``Vampire'' se tim chlubi, ze to ma naimplementovane a my tim rikame, ze jsme si to neprogramovali sami.}

@@

We employed adaptive sampling to balance
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator kept track of the number of times the problem has been tried $n_P$,
and the number of examples generated from that problem $s_P$.
The ratio $\frac{s_P}{n_P}$ corresponded to the average reward of problem $P$ observed so far.
The problems were sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
% FB: The parallelizing relaxation is not described in Auer2002. We have designed it ourselves.
\todo[author=FB]{Use some standard batching scheme instead of custom "parallelizing relaxation".}

@@

To generate a precedence for a problem,
\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit of 10 seconds was only imposed on the \Vampire{} run,
excluding the time taken by the recommender to generate the precedence.
When run with 2 threads,
the preprocessing of a single problem
took at most \num[round-mode=places,round-precision=2]{1.263048204} seconds
for \SI{80}{\percent} of the problems
by extrapolation from a sample of \num{1000} problems.\footnote{The remaining \SI{20}{\percent} of the problems either finished preprocessing within 5 seconds, or were omitted from preprocessing due to exceeding the node count limit.}
% \num[round-mode=places,round-precision=2]{4.745481158}
\todo[author=FB]{Is the footnote with maximum observed time worth the space?}
% Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
% VML-715
\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
\cref{tab:results} shows the results of the final evaluation.
